### 2013-03-28 doc/sosp13/evaluation.tex
added gups plot
Inserted UTS figure 	modified:   doc/sosp13/evaluation.tex
bunch of little things
uts eval

The goal of our evaluation is to show that the core pieces of the \Grappa
runtime system, namely our tasking system and the global memory/communication
layer work as expected and together are able to efficiently run irregular
applications. We evaluate \Grappa in three basic steps:
\begin{itemize}
\item We present results
that show that the \Grappa runtime is able to sustain very high concurrency
rates and the communication layer is able to sustain a very high rate of
global memory operations. We also show the performance of a graph kernel that
stresses communication and concurrency together.

@@

\subsection{Basic \Grappa Mechanisms}

\paragraph{User-level context switching.}
As discussed earlier, fast context switching is at the heart of \Grappa's
latency tolerance abilities. We assess context switch overheads using a simple
microbenchmark that has a configurable number of workers, where each worker 
just increments values in a large array.

@@

\begin{figure}[ht]
    \begin{center}
%      \includegraphics[width=0.5\textwidth]{figs/grappa-gups.pdf}
    \end{center}
    \caption{GUPS (giga updates per second) for \Grappa as the number of nodes grows.}
    \label{fig:grappa-gups}
\end{figure}

\paragraph{Putting it all together with Unbalanced Tree Search (UTS).}
We now show the overall performance of \Grappa running UTS. Figure~\ref{fig:grappa-uts}. The point of this experiment is to show that \Grappa's context switching and communication layers can in fact be used together to run an irregular application efficiently. Looking at the performance as the number of nodes grows shows \TODO{...}.

\begin{figure}[ht]
    \begin{center}
%      \includegraphics[width=0.5\textwidth]{figs/grappa-uts.pdf}
    \end{center}
    \caption{Vertices per second in UTS on \Grappa as the number of nodes grows.}
    \label{fig:grappa-uts}
\end{figure}
\TODO{UTS: story here is T1 class is bushy trees similar to properties
    of real world networks. Larger T1XXL (4.5 B vertices) provides
    more parallelism for continued scaling up. T3 class is deep skinny
    trees. Grappa can do no better than the straightforward UPC impl: there very little
    parallelism and the critical path is long}

@@

>>>>

The goal of our evaluation is to show that the core pieces of the \Grappa
runtime system, namely our tasking system and the global memory/communication
layer work as expected and together are able to efficiently run irregular
applications. We evaluate \Grappa in three basic steps:

\begin{itemize}

\item We present results that show that the \Grappa runtime is able to sustain
very high concurrency rates and the communication layer is able to sustain a
very high rate of global memory operations. We also show the performance of a
graph kernel that stresses communication and concurrency together.

@@

\subsection{Basic \Grappa Mechanisms}
\label{eval:basic}

\paragraph{User-level context switching.}

As discussed earlier, fast context switching is at the heart of \Grappa's
latency tolerance abilities. We assess context switch overheads using a simple
microbenchmark that has a configurable number of workers, where each worker 
just increments values in a large array.

@@

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{results/gups/gups.pdf}
    \end{center}
    \caption{GUPS (giga updates per second) for \Grappa as the number of nodes grows.}
    \label{fig:grappa-gups}
\end{figure}

\paragraph{Putting it all together with Unbalanced Tree Search in
    memory (UTS).}
We now show the overall performance of \Grappa running UTS.
Figure~\ref{fig:grappa-uts}. The point of this experiment is to
demonstrate whether \Grappa's context switching and communication layers can in fact
be used together, while balancing workload, to run an irregular application efficiently. 
We look at two classes of trees, T1x and T3x, from the
original benchmark. T1x trees are very shallow and wide, while T3x
trees are very deep. When the access to each vertex is a random
access, the critical path to search T3x trees is very long. On such
trees, we do not expect there to be sufficient concurrency for any
system, including \Grappa, to achieve high throughput. \TODO{plot it
    if time}. To verify this, at the 16-node data point, the average active tasks per
core over the search is 775 and 13 for T1XL and T3L, respectively.

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{figs/uts_scale.pdf}
    \end{center}
    \caption{Vertices per second in UTS on \Grappa as the number of nodes grows.}
    \label{fig:grappa-uts}
\end{figure}

@@

\TODO{PAGERANK:
    Without parallelizing the dot product, \Grappa cannot achieve
high utilization of workers proportional to the size of the data set.
Also mention that the cost of this is contention at the target
elements of vector.  The other parts of pagerank are super fast
(table?)
}
